---
title: "Chinook Gillnet D101 & 115 2019"
output:
  html_notebook:
    theme: united
    toc: yes
editor_options: 
  chunk_output_type: inline
---

# Introduction

## Goals & Objectives

The goal of this R Notebook is to analyze Chinook salmon mixtures from SEAK drift gillnet D101 and D115 fisheries in 2019. We have previously not looked in to these fisheries, as they target sockeye/chum, however, with stock of concern for Chilkat and Unuk + concerns about Nass/Skeena, it is worth investigating the incidental harvest of Chinook in these fisheries.

  * D101 gillnet
  * D115 gillnet

## Outline

This R Notebook will:

1) Import mixture genotypes
2) Join ASL
3) Define mixture strata
3) Data QA
4) Create *BAYES* files
5) Summarize *BAYES* results
6) Output tables

## Setup

Load *GCL-R-Functions* and all necessary packages.
```{r setup, message=FALSE, results='hide'}
source("~/../R/Functions.GCL.R")
library(tidyverse)

.username <- "krshedd"
.password <- ""
```

Read in those objects
```{r load_objects}
load_objects("../Objects/")
```


# Import mixture genotypes

Create `LocusControl` and read in genotypes from *LOKI* as `.gcl` objects. Save in directory.
```{r loki}
gillnet_sillys <- c("KGILL19D1", "KGILL19D15")
LOKI2R_GAPS.GCL(sillyvec = gillnet_sillys, username = .username, password = .password)
rm(.username, .password)

save_sillys(sillyvec = gillnet_sillys, path = "../Genotypes/original")
save_objects(objects = c("gillnet_sillys"), path = "../Objects/")
```

# Join ASL

## Gillnet

Read ASL
```{r}
gill_ASL <- read_csv(file = "../ASL Data/20190822_Gillnet_D8_11_1_15_Detailed ASL Samples.csv")

table(table(gill_ASL$`Dna Specimen No`))
```

Investigate duplicate Dna Specimen No
```{r}
gill_ASL_dups <- gill_ASL %>% 
  mutate(`Dna Specimen No` = as.character(`Dna Specimen No`)) %>% 
  count(`Dna Specimen No`) %>% 
  filter(n > 1) %>% 
  pull(`Dna Specimen No`)
```

Check for duplicates in D101
```{r}
as_tibble(KGILL19D1.gcl$attributes) %>% 
  mutate(WGC_4digit = str_sub(string = DNA_TRAY_CODE, start = 7, end = 10)) %>% 
  mutate(WGC_2digit = str_pad(string = DNA_TRAY_WELL_CODE, width = 2, side = "left", pad = "0")) %>% 
  unite(dna_specimen_no, c("WGC_4digit", "WGC_2digit"), sep = '') %>% 
  filter(dna_specimen_no %in% gill_ASL_dups)
```

Check for duplicates in D115
```{r}
as_tibble(KGILL19D15.gcl$attributes) %>% 
  mutate(WGC_4digit = str_sub(string = DNA_TRAY_CODE, start = 7, end = 10)) %>% 
  mutate(WGC_2digit = str_pad(string = DNA_TRAY_WELL_CODE, width = 2, side = "left", pad = "0")) %>% 
  unite(dna_specimen_no, c("WGC_4digit", "WGC_2digit"), sep = '') %>% 
  filter(dna_specimen_no %in% gill_ASL_dups)
```

### D101

```{r D111_gill_asl, message=FALSE}
# district and stat week counts
KGILL19D1.gcl$attributes %>% 
  mutate(`Dna Specimen No` = as.integer(paste0(str_sub(DNA_TRAY_CODE, 7, 10), str_pad(DNA_TRAY_WELL_CODE, 2, "left", "0")))) %>% 
  left_join(filter(gill_ASL, District == 101), by = "Dna Specimen No") %>% 
  count(District, `Stat Week`)
```

### D115

```{r D108_gill_asl, message=FALSE}
# district and stat week counts
KGILL19D15.gcl$attributes %>% 
  mutate(`Dna Specimen No` = as.integer(paste0(str_sub(DNA_TRAY_CODE, 7, 10), str_pad(DNA_TRAY_WELL_CODE, 2, "left", "0")))) %>% 
  left_join(filter(gill_ASL, District == 115), by = "Dna Specimen No") %>% 
  count(District, `Stat Week`)
```

# Define mixture strata

Each District and gear type
```{r}
D101Gill_2019.gcl <- KGILL19D1.gcl
D115Gill_2019.gcl <- KGILL19D15.gcl

gillnet_mixnames <- c("D101Gill_2019", "D115Gill_2019")
```

Check sample sizes
```{r}
sapply(gillnet_mixnames, function(mix) {get(paste0(mix, ".gcl"))$n})
```


# Data QA

Standard data QA:

  * Remove fish missing <80% genotypes
  * Remove duplicates (>95% genotype concordance)

```{r QA}
# original sample sizes
gillnet_sample_sizes <- tibble(silly = gillnet_mixnames,
                           genotyped = sapply(gillnet_mixnames, function(x) {get(paste0(x, ".gcl"))$n }))

# missing
gillnet_missing <- RemoveIndMissLoci.GCL(sillyvec = gillnet_mixnames, proportion = 0.8)
save_objects("gillnet_missing", "../Objects/")

gillnet_sample_sizes <- gillnet_sample_sizes %>% 
  mutate(missing = genotyped - sapply(gillnet_mixnames, function(x) {get(paste0(x, ".gcl"))$n }))

# duplicate
gillnet_duplicates <- CheckDupWithinSilly.GCL(sillyvec = gillnet_mixnames, loci = GAPSLoci_reordered, quantile = NULL, minproportion = 0.95)
gillnet_duplicates_summary <- sapply(gillnet_mixnames, function(x) {gillnet_duplicates[[x]]$report})
gillnet_duplicates_summary
save_objects("gillnet_duplicates_summary", "../Objects/")

gillnet_duplciates_removed <- RemoveDups.GCL(dupcheck = gillnet_duplicates)

gillnet_sample_sizes <- gillnet_sample_sizes %>% 
  mutate(duplicate = genotyped - missing - sapply(gillnet_mixnames, function(x) {get(paste0(x, ".gcl"))$n }))

# final
gillnet_sample_sizes <- gillnet_sample_sizes %>% 
  mutate(final = sapply(gillnet_mixnames, function(x) {get(paste0(x, ".gcl"))$n }))
gillnet_sample_sizes
save_objects("gillnet_sample_sizes", "../Objects/")

write_csv(gillnet_sample_sizes, "../Tables/gillnet_sample_sizes.csv")
```

Save post-QA genotypes
```{r post_QA}
save_sillys(sillyvec = gillnet_mixnames, path = "../Genotypes/strata_postQA")
```

# Create *BAYES* files

## Directory setup

```{r BAYES_setup, results='hide'}
save_objects("gillnet_mixnames", "../Objects/")
```

## Create mixtures

Create gillnet *BAYES* mixture files.
```{r BAYES_mixtures}
sapply(gillnet_mixnames, function(mix) {
  CreateMixture.GCL(sillys = mix, loci = GAPSLoci_reordered, IDs = NULL, mixname = mix, dir = "../BAYES/Mixture", type = "BAYES", PT = FALSE)
} )
```

## Create priors

New this year, as last year, I will be analyzing **ALL** Chinook mixtures with the full 33 reporting groups, including gillnet. However, since we have never run either of these mixtures before, what to do for a prior? Going with flat.

My plan is to keep the same prior for the gillnet groups and then spread out the "Other" evenly across all other non-gillnet reporting groups.
Now get 2018 esimates for Sport D111 + Gillnet 108 and 111
```{r}
flat_prior <- Prior.GCL(groupvec = GroupVec33RG_357, groupweights = rep(1/33, 33))
save_objects("flat_prior", "../Objects/")
```

## Create control files

Now that we have priors, just need to create *BAYES* control files.
```{r BAYES_control}
sapply(gillnet_mixnames, function(mix) {
  CreateControlFile.GCL(
    sillyvec = SEAKPops357,
    loci = GAPSLoci_reordered,
    mixname = mix,
    basename = "GAPS357pops13loci",
    suffix = "",
    nreps = 40000,
    nchains = 5,
    groupvec = GroupVec33RG_357,
    priorvec = flat_prior,
    initmat = GAPS357PopsInits,
    dir = "../BAYES/Control",
    seeds = WASSIPSockeyeSeeds,
    thin = c(1, 1, 100),
    mixfortran = mixfortran,
    basefortran = bayesfortran_357,
    switches = "F T F T T T F"
  )
})
```

## Create output directories

```{r BAYES_output}
sapply(gillnet_mixnames, function(mix) {dir.create(paste0("../BAYES/Output/", mix))} )
```

# Summarize *BAYES* results

Summarize results for both the full 33 reporting groups, the 5 gillnet groups, 3 gillnet groups, and 2 gillnet groups.

## 33 reporting groups

Create standard summary and tall tibble, save both.
```{r BAYES_summarise_33RG}
# full 33 reporting groups
gillnet_2019_33RG_EstimatesStats <- 
  CustomCombineBAYESOutput.GCL(groupvec = 1:33, groupnames = GroupNames33, maindir = "../BAYES/Output", mixvec = gillnet_mixnames,
                               prior = "", ext = "RGN", nchains = 5, burn = 0.5, alpha = 0.1, PosteriorOutput = FALSE)

# make in to a tidy tibble (tall)
gillnet_2019_33RG_estimates.tdy <- 
  bind_rows(
    lapply(gillnet_mixnames, function(mix) {  # loop over mixture names
      gillnet_2019_33RG_EstimatesStats[[mix]] %>%  # for each matrix
        as_tibble(rownames = "group") %>%  # make tibble with rownames as group
        mutate(mixname = mix) %>%  # make column for mixname
        mutate(n_group = n_distinct(group))  # make column for number of groups
    } )
  ) %>% 
  gather(estimator, value, -mixname, -group, - n_group) %>%  # gather all estimators
  separate(mixname, c("mix", "year"), sep = "_", remove = FALSE) %>%  # extract mixture and year
  separate(mix, c("district", "gear"), sep = 4) %>%  # extract district and gear
  mutate(district = as.integer(str_sub(district, 2, 4))) %>%   # make district integer
  mutate(estimator = factor(estimator, c("mean", "sd", "5%", "95%", "median", "P=0", "GR"))) %>%  # factor for ordering
  mutate(group = factor(group, GroupNames33))  # factor for ordering

save_objects(c("gillnet_2019_33RG_EstimatesStats", "gillnet_2019_33RG_estimates.tdy"), "../Estimates objects")
```

## 5 gillnet reporting groups

Need to create a new groupvec to go from 33 reporting groups to the 5 gillnet reporting groups.
```{r BAYES_summarise_5RG}
gillnet_2019_5RG_EstimatesStats <- 
  CustomCombineBAYESOutput.GCL(groupvec = GroupVec33RG_to5RG, groupnames = GroupNames5, maindir = "../BAYES/Output", mixvec = gillnet_mixnames,
                               prior = "", ext = "RGN", nchains = 5, burn = 0.5, alpha = 0.1, PosteriorOutput = FALSE)

# make in to a tidy tibble (tall)
gillnet_2019_5RG_estimates.tdy <- 
  bind_rows(
    lapply(gillnet_mixnames, function(mix) {  # loop over mixture names
      gillnet_2019_5RG_EstimatesStats[[mix]] %>%  # for each matrix
        as_tibble(rownames = "group") %>%  # make tibble with rownames as group
        mutate(mixname = mix) %>%  # make column for mixname
        mutate(n_group = n_distinct(group))  # make column for number of groups
    } )
  ) %>% 
  gather(estimator, value, -mixname, -group, - n_group) %>%  # gather all estimators
  separate(mixname, c("mix", "year"), sep = "_", remove = FALSE) %>%  # extract mixture and year
  separate(mix, c("district", "gear"), sep = 4) %>%  # extract district and gear
  mutate(district = as.integer(str_sub(district, 2, 4))) %>%   # make district integer
  mutate(estimator = factor(estimator, c("mean", "sd", "5%", "95%", "median", "P=0", "GR"))) %>%  # factor for ordering
  mutate(group = factor(group, GroupNames5))  # factor for ordering

save_objects(c("gillnet_2019_5RG_EstimatesStats", "gillnet_2019_5RG_estimates.tdy"), "../Estimates objects")

write_csv(gillnet_2019_5RG_estimates.tdy, "../Estimates tables tidy/gillnet_2019_5RG_estimates.csv")
```

## 8 driver stock reporting groups

Need to create a new groupvec to go from 33 reporting groups to the 3 gillnet reporting groups.
```{r BAYES_summarise_3RG}
gillnet_2019_8RG_EstimatesStats <- 
  CustomCombineBAYESOutput.GCL(groupvec = GroupVec33RG_to8RG, groupnames = GroupNames8, maindir = "../BAYES/Output", mixvec = gillnet_mixnames,
                               prior = "", ext = "RGN", nchains = 5, burn = 0.5, alpha = 0.1, PosteriorOutput = FALSE)

# make in to a tidy tibble (tall)
gillnet_2019_8RG_estimates.tdy <- 
  bind_rows(
    lapply(gillnet_mixnames, function(mix) {  # loop over mixture names
      gillnet_2019_8RG_EstimatesStats[[mix]] %>%  # for each matrix
        as_tibble(rownames = "group") %>%  # make tibble with rownames as group
        mutate(mixname = mix) %>%  # make column for mixname
        mutate(n_group = n_distinct(group))  # make column for number of groups
    } )
  ) %>% 
  gather(estimator, value, -mixname, -group, - n_group) %>%  # gather all estimators
  separate(mixname, c("mix", "year"), sep = "_", remove = FALSE) %>%  # extract mixture and year
  separate(mix, c("district", "gear"), sep = 4) %>%  # extract district and gear
  mutate(district = as.integer(str_sub(district, 2, 4))) %>%   # make district integer
  mutate(estimator = factor(estimator, c("mean", "sd", "5%", "95%", "median", "P=0", "GR"))) %>%  # factor for ordering
  mutate(group = factor(group, GroupNames8))  # factor for ordering

save_objects(c("gillnet_2019_8RG_EstimatesStats", "gillnet_2019_8RG_estimates.tdy"), "../Estimates objects")
```

## 18 gillnet reporting groups

Need to create a new groupvec to go from 33 reporting groups to the 2 gillnet reporting groups.
```{r BAYES_summarise_2RG}
gillnet_2019_18RG_EstimatesStats <- 
  CustomCombineBAYESOutput.GCL(groupvec = GroupVec33RG_to18RG, groupnames = GroupNames18, maindir = "../BAYES/Output", mixvec = gillnet_mixnames,
                               prior = "", ext = "RGN", nchains = 5, burn = 0.5, alpha = 0.1, PosteriorOutput = FALSE)

# make in to a tidy tibble (tall)
gillnet_2019_18RG_estimates.tdy <- 
  bind_rows(
    lapply(gillnet_mixnames, function(mix) {  # loop over mixture names
      gillnet_2019_18RG_EstimatesStats[[mix]] %>%  # for each matrix
        as_tibble(rownames = "group") %>%  # make tibble with rownames as group
        mutate(mixname = mix) %>%  # make column for mixname
        mutate(n_group = n_distinct(group))  # make column for number of groups
    } )
  ) %>% 
  gather(estimator, value, -mixname, -group, - n_group) %>%  # gather all estimators
  separate(mixname, c("mix", "year"), sep = "_", remove = FALSE) %>%  # extract mixture and year
  separate(mix, c("district", "gear"), sep = 4) %>%  # extract district and gear
  mutate(district = as.integer(str_sub(district, 2, 4))) %>%   # make district integer
  mutate(estimator = factor(estimator, c("mean", "sd", "5%", "95%", "median", "P=0", "GR"))) %>%  # factor for ordering
  mutate(group = factor(group, GroupNames18))  # factor for ordering

save_objects(c("gillnet_2019_18RG_EstimatesStats", "gillnet_2019_18RG_estimates.tdy"), "../Estimates objects")
```

# Output tables

## Gelman-Rubin

Need to check Gelman-Rubin first to verify that all estimates are < 1.2 for 5 gillnet reporting groups.
```{r GR_check}
all(gillnet_2019_33RG_estimates.tdy %>% filter(estimator == "GR") %>% pull(value) < 1.2)
```

## Estimates

Great, now that we know our data converged for the 5 gillnet reporting groups, we can summarise the tall, tidy, tibble for the summary spreadsheet for each mixture and reporting group combination.

```{r 5RG_estimates}
gillnet_2019_5RG_EstimatesStats
```

```{r}
gillnet_sample_sizes
```


### Gill D101 33RG

Show results where the upper bound of the 90% CI included 5%.
```{r}
sapply(gillnet_2019_33RG_EstimatesStats, function(x) {as_tibble(x = x, rownames = "group")}, simplify = FALSE) %>% 
  bind_rows(.id = "mixname") %>% 
  group_by(mixname) %>% 
  filter(`95%` >= 0.05) %>% 
  arrange(mixname, desc(mean))
```

