---
title: "Chinook TBR 2019"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

# Introduction

## Goals & Objectives

The goal of this R Notebook is to analyze Chinook salmon mixtures from SEAK TBR fisheries in 2019. Given sport fishing restrictions this year, we are doing all 4 mixtures, but some are pretty sad (low sample size):

  * D108 sport
  * D111 sport
  * D108 gillnet
  * D111 gillnet

Also new this year, Randy Peterson asked to break out the *Other* reporting group in to:

  * *Other SEAK*
  * *Canada*
  * *Southern US (SUS)*

Correction, Randy admitted that this wasn't necessary on 10/30/18, so not going to bother this year.

## Outline

This R Notebook will:

1) Import mixture genotypes
2) Join ASL
3) Define mixture strata
3) Data QA
4) Create *BAYES* files
5) Summarize *BAYES* results
6) Output tables

## Setup

Load *GCL-R-Functions* and all necessary packages.
```{r setup, message=FALSE, results='hide'}
source("~/../R/Functions.GCL.R")
library(tidyverse)

.username <- "krshedd"
.password <- ""
```

Copy over necessary objects from previous year (i.e. *groupvec*)
```{r copy, results='hide'}
SEAK18_objects_copy <- c(list.files(path = "../../SEAK18/Objects/", pattern = "Group", full.names = TRUE),
                         list.files(path = "../../SEAK18/Objects/", pattern = "GAPS", full.names = TRUE))
file.copy(from = SEAK18_objects_copy, to = "../Objects/")
```

Read in those objects
```{r load_objects}
load_objects("../Objects/")
```


# Import mixture genotypes

Create `LocusControl` and read in genotypes from *LOKI* as `.gcl` objects. Save in directory.
```{r loki}
TBR_sillys <- c("KGILL19D8", "KGILL19D11", "KSPORT19")
LOKI2R_GAPS.GCL(sillyvec = TBR_sillys, username = .username, password = .password)
rm(.username, .password)

dir.create("../Genotypes")
dir.create("../Genotypes/original")
save_sillys(sillyvec = TBR_sillys, path = "../Genotypes/original")
save_objects(objects = c("LocusControl", "TBR_sillys"), path = "../Objects/")
```

# Join ASL

## Sport

Read in the sport ASL data and join with attributes to verify that we only have large fish (>660mm) caught between stat week 17-29 from D111.
```{r sport_asl, message=FALSE}
sport_ASL <- read_csv(file = "../ASL Data/_2019_SEAK_SF_Whatman_AWL_31JUL19.csv")

# district and stat week counts
KSPORT19.gcl$attributes <- KSPORT19.gcl$attributes %>% 
  mutate(DNA_TRAY_CODE = as.integer(DNA_TRAY_CODE)) %>% 
  left_join(sport_ASL, by = c("DNA_TRAY_CODE" = "Whatman_Card", "DNA_TRAY_WELL_CODE" = "SAMPLE_NO"))

KSPORT19.gcl$attributes %>% 
  count(DISTRICT, STATWEEK)

# all large fish?
KSPORT19.gcl$attributes %>% 
  summarise(min(LENGTH))
```

## Gillnet

### D111
Read in the gillnet ASL data and join with attributes to verify that we only have large fish (>660mm) caught between stat week 17-29 from D111.
```{r D111_gill_asl, message=FALSE}
gill_ASL <- read_csv(file = "../ASL Data/20190822_Gillnet_D8_11_1_15_Detailed ASL Samples.csv")

# district and stat week counts
KGILL19D11.gcl$attributes %>% 
  mutate(`Dna Specimen No` = as.integer(paste0(str_sub(DNA_TRAY_CODE, 7, 10), str_pad(DNA_TRAY_WELL_CODE, 2, "left", "0")))) %>% 
  left_join(gill_ASL, by = "Dna Specimen No") %>% 
  count(District, `Stat Week`)

# all large fish?
KGILL19D11.gcl$attributes %>% 
  mutate(`Dna Specimen No` = as.integer(paste0(str_sub(DNA_TRAY_CODE, 7, 10), str_pad(DNA_TRAY_WELL_CODE, 2, "left", "0")))) %>% 
  left_join(gill_ASL, by = "Dna Specimen No") %>% 
  summarise(min(`Average Length mm`))
```

### D108
Verify that we only have large fish (>660mm) caught between stat week 17-29 from D108. *Note* there are duplicate `Dna Specimen No` between 101 and 108...thus the filter.
```{r D108_gill_asl, message=FALSE}
# district and stat week counts
KGILL19D8.gcl$attributes %>% 
  mutate(`Dna Specimen No` = as.integer(paste0(str_sub(DNA_TRAY_CODE, 7, 10), str_pad(DNA_TRAY_WELL_CODE, 2, "left", "0")))) %>% 
  left_join(filter(gill_ASL, District == 108), by = "Dna Specimen No") %>% 
  count(District, `Stat Week`)

# all large fish?
KGILL19D8.gcl$attributes %>% 
  mutate(`Dna Specimen No` = as.integer(paste0(str_sub(DNA_TRAY_CODE, 7, 10), str_pad(DNA_TRAY_WELL_CODE, 2, "left", "0")))) %>% 
  left_join(filter(gill_ASL, District == 108), by = "Dna Specimen No") %>% 
  summarise(min(`Average Length mm`))
```

All fish genotyped are large fish (>660mm) from stat week 17-29, and appropriate districts. Good to go.

# Define mixture strata

Each District and gear type
```{r}
D108Gill_2019.gcl <- KGILL19D8.gcl
D111Gill_2019.gcl <- KGILL19D11.gcl

D108Sport_2019.vials <- setNames(object = list(AttributesToIDs.GCL(silly = "KSPORT19", attribute = "DISTRICT", matching = 108)), nm = "KSPORT19")
PoolCollections.GCL(collections = "KSPORT19", loci = GAPSLoci_reordered, IDs = D108Sport_2019.vials, newname = "D108Sport_2019")

D111Sport_2019.vials <- setNames(object = list(AttributesToIDs.GCL(silly = "KSPORT19", attribute = "DISTRICT", matching = 111)), nm = "KSPORT19")
PoolCollections.GCL(collections = "KSPORT19", loci = GAPSLoci_reordered, IDs = D111Sport_2019.vials, newname = "D111Sport_2019")

TBR_mixnames <- c("D108Gill_2019", "D111Gill_2019", "D108Sport_2019", "D111Sport_2019")
```

Check sample sizes
```{r}
sapply(TBR_mixnames, function(mix) {get(paste0(mix, ".gcl"))$n})
```


# Data QA

Standard data QA:

  * Remove fish missing <80% genotypes
  * Remove duplicates (>95% genotype concordance)

```{r QA}
# original sample sizes
TBR_sample_sizes <- tibble(silly = TBR_mixnames,
                           genotyped = sapply(TBR_mixnames, function(x) {get(paste0(x, ".gcl"))$n }))

# missing
TBR_missing <- RemoveIndMissLoci.GCL(sillyvec = TBR_mixnames, proportion = 0.8)
save_objects("TBR_missing", "../Objects/")

TBR_sample_sizes <- TBR_sample_sizes %>% 
  mutate(missing = genotyped - sapply(TBR_mixnames, function(x) {get(paste0(x, ".gcl"))$n }))

# duplicate
TBR_duplicates <- CheckDupWithinSilly.GCL(sillyvec = TBR_mixnames, loci = GAPSLoci_reordered, quantile = NULL, minproportion = 0.95)
TBR_duplicates_summary <- sapply(TBR_mixnames, function(x) {TBR_duplicates[[x]]$report})
TBR_duplicates_summary
save_objects("TBR_duplicates_summary", "../Objects/")

TBR_duplciates_removed <- RemoveDups.GCL(dupcheck = TBR_duplicates)

TBR_sample_sizes <- TBR_sample_sizes %>% 
  mutate(duplicate = genotyped - missing - sapply(TBR_mixnames, function(x) {get(paste0(x, ".gcl"))$n }))

# final
TBR_sample_sizes <- TBR_sample_sizes %>% 
  mutate(final = sapply(TBR_mixnames, function(x) {get(paste0(x, ".gcl"))$n }))
TBR_sample_sizes
save_objects("TBR_sample_sizes", "../Objects/")

dir.create("../Tables")
write_csv(TBR_sample_sizes, "../Tables/TBR_sample_sizes.csv")
```

Save post-QA genotypes
```{r post_QA}
dir.create("../Genotypes/strata_postQA")
save_sillys(sillyvec = TBR_mixnames, path = "../Genotypes/strata_postQA")
```

# Create *BAYES* files

## Directory setup

First need to set up *BAYES* directory structure and copy over baseline file and *BAYES* objects.
```{r BAYES_setup, results='hide'}
dir.create(path = "../BAYES")
sapply(c("Baseline", "Control", "Mixture", "Output"), function(folder) {dir.create(path = paste("../BAYES", folder, sep = "/"))} )

file.copy(from = "V:/Analysis/1_SEAK/Chinook/Baseline/GAPS3.0/Objects/SEAKPops357.txt", to = "../Objects")
file.copy(from = "V:/Analysis/1_SEAK/Chinook/Baseline/GAPS3.0/Objects/bayesfortran_357.txt", to = "../Objects")
file.copy(from = "V:/Analysis/1_SEAK/Chinook/Baseline/GAPS3.0/BAYES/Baseline/GAPS357pops13loci.bse", to = "../BAYES/Baseline")
file.copy(from = "V:/Analysis/4_Westward/Sockeye/KMA Commercial Harvest 2014-2016/Mixtures/Objects/WASSIPSockeyeSeeds.txt", to = "../Objects")

save_objects("TBR_mixnames", "../Objects/")
load_objects("../Objects/")
```

## Create mixtures

Save the fortran format and create TBR *BAYES* mixture files.
```{r BAYES_mixtures}
mixfortran <- CreateMixture.GCL(sillys = TBR_mixnames[1], loci = GAPSLoci_reordered, IDs = NULL, mixname = TBR_mixnames[1], dir = "../BAYES/Mixture", type = "BAYES", PT = FALSE)
save_objects("mixfortran", "../Objects/")

sapply(TBR_mixnames, function(mix) {
  CreateMixture.GCL(sillys = mix, loci = GAPSLoci_reordered, IDs = NULL, mixname = mix, dir = "../BAYES/Mixture", type = "BAYES", PT = FALSE)
} )
```

## Create priors

New this year, as last year, I will be analyzing **ALL** Chinook mixtures with the full 33 reporting groups, including TBR. However, since we didn't run D108 Sport last year, I need to go back to 2017 when we ran TBR mixtures for just the 5 TBR reporting groups, I will have to mess with the priors a bit.
```{r read_2017_estimates}
TBR_2017_5RG_EstimatesStats <- dget("../../SEAK17/Estimates objects/TBR_2017_5RG_EstimatesStats.txt")
TBR_2017_means <- sapply(TBR_2017_5RG_EstimatesStats, function(mix) {mix[, "mean"]})
# remove D108 sport, as we aren't running this year
TBR_2017_means <- TBR_2017_means[, str_replace(TBR_mixnames, "2019", "2017")]
TBR_2017_means
```

My plan is to keep the same prior for the TBR groups and then spread out the "Other" evenly across all other non-TBR reporting groups.
```{r setup_2019_priors}
# fill in all with "Other" spread out across remaining groups
TBR_2017_means_33RG <- matrix(data = TBR_2017_means["Other", ] / (33 - 4), 
                              nrow = 33, 
                              ncol = length(TBR_mixnames), 
                              byrow = TRUE, 
                              dimnames = list(GroupNames33, str_replace(TBR_mixnames, "2019", "2017")))

# fill in TBR groups with 2017 means
TBR_2017_means_33RG[GroupNames5[1:4], str_replace(TBR_mixnames, "2019", "2017")] <- TBR_2017_means[GroupNames5[1:4], str_replace(TBR_mixnames, "2019", "2017")]

# verify
apply(TBR_2017_means_33RG, 2, sum)
```

Now get 2018 esimates for Sport D111 + Gillnet 108 and 111
```{r}
TBR_2018_33RG_EstimatesStats <- dget("../../SEAK18/Estimates objects/TBR_2018_33RG_EstimatesStats.txt")
TBR_2018_means <- sapply(TBR_2018_33RG_EstimatesStats, function(mix) {mix[, "mean"]})
# remove D108 sport, as we aren't running this year
TBR_2018_means <- TBR_2018_means[, str_replace(TBR_mixnames[-3], "2019", "2018")]
TBR_2018_means
```

Now create 2019 priors.
```{r create_2019_priors}
TBR_priors <-
  apply(cbind(TBR_2018_means[, 1:2, drop = FALSE], 
              TBR_2017_means_33RG[, "D108Sport_2017", drop = FALSE], 
              TBR_2018_means[, 3, drop = FALSE]), 
        2, function(mix) {
    Prior.GCL(groupvec = GroupVec33RG_357,
              groupweights = mix,
              minval = 0.01)
  })
colnames(TBR_priors) <- TBR_mixnames
save_objects("TBR_priors", "../Objects/")
```

## Create control files

Now that we have priors, just need to create *BAYES* control files.
```{r BAYES_control}
sapply(TBR_mixnames, function(mix) {
  CreateControlFile.GCL(
    sillyvec = SEAKPops357,
    loci = GAPSLoci_reordered,
    mixname = mix,
    basename = "GAPS357pops13loci",
    suffix = "",
    nreps = 40000,
    nchains = 5,
    groupvec = GroupVec33RG_357,
    priorvec = TBR_priors[, mix],
    initmat = GAPS357PopsInits,
    dir = "../BAYES/Control",
    seeds = WASSIPSockeyeSeeds,
    thin = c(1, 1, 100),
    mixfortran = mixfortran,
    basefortran = bayesfortran_357,
    switches = "F T F T T T F"
  )
})
```

## Create output directories

```{r BAYES_output}
sapply(TBR_mixnames, function(mix) {dir.create(paste0("../BAYES/Output/", mix))} )
```

# Summarize *BAYES* results

Summarize results for both the full 33 reporting groups, the 5 TBR groups, 3 TBR groups, and 2 TBR groups.

## 33 reporting groups

Create standard summary and tall tibble, save both.
```{r BAYES_summarise_33RG}
# full 33 reporting groups
TBR_2018_33RG_EstimatesStats <- 
  CustomCombineBAYESOutput.GCL(groupvec = 1:33, groupnames = GroupNames33, maindir = "../BAYES/Output", mixvec = TBR_mixnames,
                               prior = "", ext = "RGN", nchains = 5, burn = 0.5, alpha = 0.1, PosteriorOutput = FALSE)

# make in to a tidy tibble (tall)
TBR_2018_33RG_estimates.tdy <- 
  bind_rows(
    lapply(TBR_mixnames, function(mix) {  # loop over mixture names
      TBR_2018_33RG_EstimatesStats[[mix]] %>%  # for each matrix
        as_tibble(rownames = "group") %>%  # make tibble with rownames as group
        mutate(mixname = mix) %>%  # make column for mixname
        mutate(n_group = n_distinct(group))  # make column for number of groups
    } )
  ) %>% 
  gather(estimator, value, -mixname, -group, - n_group) %>%  # gather all estimators
  separate(mixname, c("mix", "year"), sep = "_", remove = FALSE) %>%  # extract mixture and year
  separate(mix, c("district", "gear"), sep = 4) %>%  # extract district and gear
  mutate(district = as.integer(str_sub(district, 2, 4))) %>%   # make district integer
  mutate(estimator = factor(estimator, c("mean", "sd", "5%", "95%", "median", "P=0", "GR"))) %>%  # factor for ordering
  mutate(group = factor(group, GroupNames33))  # factor for ordering

dir.create("../Estimates objects")
save_objects(c("TBR_2018_33RG_EstimatesStats", "TBR_2018_33RG_estimates.tdy"), "../Estimates objects")
```

## 5 TBR reporting groups

Need to create a new groupvec to go from 33 reporting groups to the 5 TBR reporting groups.
```{r BAYES_summarise_5RG}
# 5 TBR reporting groups
GroupVec33RG_to5RG <- case_when(GroupNames33 == GroupNames5[1] ~ 1,
                                GroupNames33 == GroupNames5[2] ~ 2,
                                GroupNames33 == GroupNames5[3] ~ 3,
                                GroupNames33 == GroupNames5[4] ~ 4,
                                TRUE ~ 5)
save_objects("GroupVec33RG_to5RG", "../Objects/")

TBR_2018_5RG_EstimatesStats <- 
  CustomCombineBAYESOutput.GCL(groupvec = GroupVec33RG_to5RG, groupnames = GroupNames5, maindir = "../BAYES/Output", mixvec = TBR_mixnames,
                               prior = "", ext = "RGN", nchains = 5, burn = 0.5, alpha = 0.1, PosteriorOutput = FALSE)

# make in to a tidy tibble (tall)
TBR_2018_5RG_estimates.tdy <- 
  bind_rows(
    lapply(TBR_mixnames, function(mix) {  # loop over mixture names
      TBR_2018_5RG_EstimatesStats[[mix]] %>%  # for each matrix
        as_tibble(rownames = "group") %>%  # make tibble with rownames as group
        mutate(mixname = mix) %>%  # make column for mixname
        mutate(n_group = n_distinct(group))  # make column for number of groups
    } )
  ) %>% 
  gather(estimator, value, -mixname, -group, - n_group) %>%  # gather all estimators
  separate(mixname, c("mix", "year"), sep = "_", remove = FALSE) %>%  # extract mixture and year
  separate(mix, c("district", "gear"), sep = 4) %>%  # extract district and gear
  mutate(district = as.integer(str_sub(district, 2, 4))) %>%   # make district integer
  mutate(estimator = factor(estimator, c("mean", "sd", "5%", "95%", "median", "P=0", "GR"))) %>%  # factor for ordering
  mutate(group = factor(group, GroupNames5))  # factor for ordering

save_objects(c("TBR_2018_5RG_EstimatesStats", "TBR_2018_5RG_estimates.tdy"), "../Estimates objects")

dir.create("../Estimates tables tidy")
write_csv(TBR_2018_5RG_estimates.tdy, "../Estimates tables tidy/TBR_2018_5RG_estimates.csv")
```

## 3 TBR reporting groups

Need to create a new groupvec to go from 33 reporting groups to the 3 TBR reporting groups.
```{r BAYES_summarise_3RG}
# 3 TBR reporting groups
GroupVec33RG_to3RG <- case_when(GroupNames33 == GroupNames5[1] ~ 1,
                                GroupNames33 == GroupNames5[2] ~ 2,
                                GroupNames33 == GroupNames5[3] ~ 1,
                                GroupNames33 == GroupNames5[4] ~ 3,
                                TRUE ~ 3)
save_objects("GroupVec33RG_to3RG", "../Objects/")

TBR_2018_3RG_EstimatesStats <- 
  CustomCombineBAYESOutput.GCL(groupvec = GroupVec33RG_to3RG, groupnames = GroupNames3, maindir = "../BAYES/Output", mixvec = TBR_mixnames,
                               prior = "", ext = "RGN", nchains = 5, burn = 0.5, alpha = 0.1, PosteriorOutput = FALSE)

# make in to a tidy tibble (tall)
TBR_2018_3RG_estimates.tdy <- 
  bind_rows(
    lapply(TBR_mixnames, function(mix) {  # loop over mixture names
      TBR_2018_3RG_EstimatesStats[[mix]] %>%  # for each matrix
        as_tibble(rownames = "group") %>%  # make tibble with rownames as group
        mutate(mixname = mix) %>%  # make column for mixname
        mutate(n_group = n_distinct(group))  # make column for number of groups
    } )
  ) %>% 
  gather(estimator, value, -mixname, -group, - n_group) %>%  # gather all estimators
  separate(mixname, c("mix", "year"), sep = "_", remove = FALSE) %>%  # extract mixture and year
  separate(mix, c("district", "gear"), sep = 4) %>%  # extract district and gear
  mutate(district = as.integer(str_sub(district, 2, 4))) %>%   # make district integer
  mutate(estimator = factor(estimator, c("mean", "sd", "5%", "95%", "median", "P=0", "GR"))) %>%  # factor for ordering
  mutate(group = factor(group, GroupNames3))  # factor for ordering

save_objects(c("TBR_2018_3RG_EstimatesStats", "TBR_2018_3RG_estimates.tdy"), "../Estimates objects")
```

## 2 TBR reporting groups

Need to create a new groupvec to go from 33 reporting groups to the 2 TBR reporting groups.
```{r BAYES_summarise_2RG}
# 2 TBR reporting groups
GroupVec33RG_to2RG <- case_when(GroupNames33 == GroupNames5[1] ~ 1,
                                GroupNames33 == GroupNames5[2] ~ 2,
                                GroupNames33 == GroupNames5[3] ~ 1,
                                GroupNames33 == GroupNames5[4] ~ 2,
                                TRUE ~ 2)
save_objects("GroupVec33RG_to2RG", "../Objects/")

TBR_2018_2RG_EstimatesStats <- 
  CustomCombineBAYESOutput.GCL(groupvec = GroupVec33RG_to2RG, groupnames = GroupNames2, maindir = "../BAYES/Output", mixvec = TBR_mixnames,
                               prior = "", ext = "RGN", nchains = 5, burn = 0.5, alpha = 0.1, PosteriorOutput = FALSE)

# make in to a tidy tibble (tall)
TBR_2018_2RG_estimates.tdy <- 
  bind_rows(
    lapply(TBR_mixnames, function(mix) {  # loop over mixture names
      TBR_2018_2RG_EstimatesStats[[mix]] %>%  # for each matrix
        as_tibble(rownames = "group") %>%  # make tibble with rownames as group
        mutate(mixname = mix) %>%  # make column for mixname
        mutate(n_group = n_distinct(group))  # make column for number of groups
    } )
  ) %>% 
  gather(estimator, value, -mixname, -group, - n_group) %>%  # gather all estimators
  separate(mixname, c("mix", "year"), sep = "_", remove = FALSE) %>%  # extract mixture and year
  separate(mix, c("district", "gear"), sep = 4) %>%  # extract district and gear
  mutate(district = as.integer(str_sub(district, 2, 4))) %>%   # make district integer
  mutate(estimator = factor(estimator, c("mean", "sd", "5%", "95%", "median", "P=0", "GR"))) %>%  # factor for ordering
  mutate(group = factor(group, GroupNames2))  # factor for ordering

save_objects(c("TBR_2018_2RG_EstimatesStats", "TBR_2018_2RG_estimates.tdy"), "../Estimates objects")
```

# Output tables

Need to add data to the exisiting "D8&11 Estimates" summary spreadsheet. 

## Gelman-Rubin

Need to check Gelman-Rubin first to verify that all estimates are < 1.2 for 5 TBR reporting groups.
```{r GR_check}
all(TBR_2018_5RG_estimates.tdy %>% filter(estimator == "GR") %>% pull(value) < 1.2)
```

## Estimates

Great, now that we know our data converged for the 5 TBR reporting groups, we can summarise the tall, tidy, tibble for the summary spreadsheet for each mixture and reporting group combination.

```{r 5RG_estimates}
TBR_2018_5RG_EstimatesStats
```


### Gill D108 5RG

```{r D108Gill_5RG}
TBR_2018_5RG_estimates.tdy %>% 
  filter(n_group == 5) %>%  # want 5RG
  filter(estimator %in% c("mean", "sd", "5%", "95%")) %>%  # only relevant estimators
  filter(mixname == "D108Gill_2018") %>%  # specify mixture
  spread(group, value) %>%  # wide
  select(GroupNames5) %>%  # toss other varialbes
  write.table('clipboard', sep = '\t', row.names = FALSE, col.names = FALSE)  # copy to clipboard
```

### Gill D108 3RG

```{r D108Gill_3RG}
TBR_2018_3RG_estimates.tdy %>% 
  filter(n_group == 3) %>%  # want 3RG
  filter(estimator %in% c("mean", "sd", "5%", "95%")) %>%  # only relevant estimators
  filter(mixname == "D108Gill_2018") %>%  # specify mixture
  spread(group, value) %>%  # wide
  select(GroupNames3) %>%  # toss other varialbes
  write.table('clipboard', sep = '\t', row.names = FALSE, col.names = FALSE)  # copy to clipboard
```

### Gill D108 2RG

```{r D108Gill_2RG}
TBR_2018_2RG_estimates.tdy %>% 
  filter(n_group == 2) %>%  # want 5RG
  filter(estimator %in% c("mean", "sd", "5%", "95%")) %>%  # only relevant estimators
  filter(mixname == "D108Gill_2018") %>%  # specify mixture
  spread(group, value) %>%  # wide
  select(GroupNames2) %>%  # toss other varialbes
  write.table('clipboard', sep = '\t', row.names = FALSE, col.names = FALSE)  # copy to clipboard
```

### Gill D111 5RG

```{r D111Gill_5RG}
TBR_2018_5RG_estimates.tdy %>% 
  filter(n_group == 5) %>%  # want 5RG
  filter(estimator %in% c("mean", "sd", "5%", "95%")) %>%  # only relevant estimators
  filter(mixname == "D111Gill_2018") %>%  # specify mixture
  spread(group, value) %>%  # wide
  select(GroupNames5) %>%  # toss other varialbes
  write.table('clipboard', sep = '\t', row.names = FALSE, col.names = FALSE)  # copy to clipboard
```

### Gill D111 3RG

```{r D111Gill_3RG}
TBR_2018_3RG_estimates.tdy %>% 
  filter(n_group == 3) %>%  # want 3RG
  filter(estimator %in% c("mean", "sd", "5%", "95%")) %>%  # only relevant estimators
  filter(mixname == "D111Gill_2018") %>%  # specify mixture
  spread(group, value) %>%  # wide
  select(GroupNames3) %>%  # toss other varialbes
  write.table('clipboard', sep = '\t', row.names = FALSE, col.names = FALSE)  # copy to clipboard
```

### Gill D111 2RG

```{r D111Gill_2RG}
TBR_2018_2RG_estimates.tdy %>% 
  filter(n_group == 2) %>%  # want 5RG
  filter(estimator %in% c("mean", "sd", "5%", "95%")) %>%  # only relevant estimators
  filter(mixname == "D111Gill_2018") %>%  # specify mixture
  spread(group, value) %>%  # wide
  select(GroupNames2) %>%  # toss other varialbes
  write.table('clipboard', sep = '\t', row.names = FALSE, col.names = FALSE)  # copy to clipboard
```

### Sport D111 5RG

```{r D111Sport_5RG}
TBR_2018_5RG_estimates.tdy %>% 
  filter(n_group == 5) %>%  # want 5RG
  filter(estimator %in% c("mean", "sd", "5%", "95%")) %>%  # only relevant estimators
  filter(mixname == "D111Sport_2018") %>%  # specify mixture
  spread(group, value) %>%  # wide
  select(GroupNames5) %>%  # toss other varialbes
  write.table('clipboard', sep = '\t', row.names = FALSE, col.names = FALSE)  # copy to clipboard
```

### Sport D111 3RG

```{r D111Sport_3RG}
TBR_2018_3RG_estimates.tdy %>% 
  filter(n_group == 3) %>%  # want 3RG
  filter(estimator %in% c("mean", "sd", "5%", "95%")) %>%  # only relevant estimators
  filter(mixname == "D111Sport_2018") %>%  # specify mixture
  spread(group, value) %>%  # wide
  select(GroupNames3) %>%  # toss other varialbes
  write.table('clipboard', sep = '\t', row.names = FALSE, col.names = FALSE)  # copy to clipboard
```

### Sport D111 2RG

```{r D111Sport_2RG}
TBR_2018_2RG_estimates.tdy %>% 
  filter(n_group == 2) %>%  # want 5RG
  filter(estimator %in% c("mean", "sd", "5%", "95%")) %>%  # only relevant estimators
  filter(mixname == "D111Sport_2018") %>%  # specify mixture
  spread(group, value) %>%  # wide
  select(GroupNames2) %>%  # toss other varialbes
  write.table('clipboard', sep = '\t', row.names = FALSE, col.names = FALSE)  # copy to clipboard
```

## ASL metadata

The summary spreadsheet has tabs for "Gill_SampleInfo" and "Sport_SampleInfo" that has the ASL data for all TBR fish run since 2004. Need to add the ASL metadata from this year as well.

### Gillnet

Read in gillnet ASL data for extracted fish and add to spreadsheet, then re-do pivot table.
```{r gill_metadata}
# join extraction asl with fish passing QA, select columns, copy to clipboard
TBR_gill_ASL.tib %>% 
  mutate(Subdistrict = str_sub(District, 5, 6)) %>% 
  mutate(SizeClass = case_when(`Average Length mm` >= 660 ~ "LARGE",
                               `Average Length mm` < 660 ~ "SMALL")) %>% 
  right_join(
    bind_rows(
      KGILL19D8.gcl$attributes %>% 
        mutate(WGC4digit = str_sub(DNA_TRAY_CODE, 7, 10)) %>% 
        mutate(WGC2digit = str_pad(DNA_TRAY_WELL_CODE, 2, "left", "0")) %>% 
        unite("Dna Specimen No", c(WGC4digit, WGC2digit), sep = "") %>% 
        mutate(`Dna Specimen No` = as.integer(`Dna Specimen No`)) %>% 
        select(`Dna Specimen No`),
      KGILL19D11.gcl$attributes %>% 
        mutate(WGC4digit = str_sub(DNA_TRAY_CODE, 7, 10)) %>% 
        mutate(WGC2digit = str_pad(DNA_TRAY_WELL_CODE, 2, "left", "0")) %>% 
        unite("Dna Specimen No", c(WGC4digit, WGC2digit), sep = "") %>% 
        mutate(`Dna Specimen No` = as.integer(`Dna Specimen No`)) %>% 
        select(`Dna Specimen No`)
    )
    , by = "Dna Specimen No") %>% 
  select(Year, `Sample Date`, `Stat Week`, `Port Code`, District, Subdistrict, `Average Length mm`, SizeClass, `Dna Specimen No`) %>% 
  write.table('clipboard', sep = '\t', row.names = FALSE, col.names = FALSE)
```

### Sport

Read in sport ASL data for extracted fish and add to spreadsheet, then re-do pivot table.
```{r sport_metadata}
# join extraction asl with fish passing QA, select columns, copy to clipboard
TBR_sport_ASL.tib %>% 
  unite(GSI, c(Whatman_Card, SAMPLE_NO), sep = "_", remove = FALSE) %>% 
  right_join(KSPORT19.gcl$attributes %>% 
               mutate(DNA_TRAY_CODE = as.integer(DNA_TRAY_CODE)) %>% 
               unite(GSI, c(DNA_TRAY_CODE, DNA_TRAY_WELL_CODE), sep = "_", remove = FALSE)
             , by = "GSI") %>% 
  select(Year, SITE, DATE, STATWEEK, LENGTH, GSI, BIWEEK, DISTRICT, FK_FISH_ID) %>% 
  write.table('clipboard', sep = '\t', row.names = FALSE, col.names = FALSE)
```

