---
title: "Gillnet D108 Individual Assignment"
output:
  html_notebook:
    theme: united
    toc: yes
editor_options: 
  chunk_output_type: inline
---

# Purpose

Troy Thynes (area coordinator for Region 1) noted that the stock composition for Taku in Gillnet District 108 harvest was much higher than had been in the past (8% vs. <2%). What's up with this? Look at individual assignment probabilities to see if it is a lot of fish that could be Stikine...

# *ONCOR* Individual Assignment

```{r}
source("~/../R/Functions.GCL.R")
```

## Get post-QA genotypes

```{r ONCOR_genotypes}
load_sillys(path = "../Genotypes/strata_postQA/", sillyvec = "D108Gill_2019")
load_objects("../Objects/")
```

## Create *ONCOR* input files

```{r ONCOR_input}
gcl2Genepop.GCL(sillyvec = "D108Gill_2019", path = "../ONCOR/Mixture/D108Gill_2019.gen", loci = GAPSLoci, VialNums = TRUE, usat = TRUE)

# Remove "Pop" designations
# rawdat <- scan(file = "../ONCOR/Mixture/D108Gill_2019.gen", what = '', sep = '\n')
# moddat <- rawdat[-grep(pattern = "Pop", x = rawdat)[-1]]
# write.table(x = moddat, file = "../ONCOR/Mixture/D108Gill_2019.gen", quote = FALSE, row.names = FALSE, col.names = FALSE)
```

## Read *ONCOR* output

### Sport scales

Need to match up ASL data with *ONCOR* output. This is a bit of a pain in the ass, because the *ONCOR* output is by SillySource, but ASL has WGC and Sample No. Will need to `attributes` table from KSPORT18.
```{r ONCOR_sport_raw_output}
library(tidyverse)
raw_oncor <- scan(file = "../ONCOR/Output/D108Gill_2019_33RG_IA.txt", what = '', sep = '\n', blank.lines.skip = FALSE)
skip <- grep(pattern = "PROBABILITY OF EACH INDIVIDUAL IN THE MIXTURE BELONGING TO EACH REPORTING GROUP", x = raw_oncor) + 1
(D108Gill_dat <- read_delim(file = "../ONCOR/Output/D108Gill_2019_33RG_IA.txt", delim = "\t", skip = skip, trim_ws = TRUE) %>% 
    dplyr::rename(FishID = X1))
```

Sort by Taku probability.
```{r}
D108Gill_dat %>% 
  arrange(desc(Taku))
```

Only three fish that we are pretty confident came from Taku + maybe one more that is most likely Taku. Lots of fish with relatively small probability of being from Taku pushed the stock composition higher.