---
title: "Winter Troll GSI Plots AY 2019"
output:
  html_notebook:
    theme: united
    toc: yes
editor_options: 
  chunk_output_type: inline
---

```{r setup, message=FALSE, results='hide'}
knitr::opts_chunk$set(echo = FALSE)
source("~/../R/Functions.GCL.R")
library(tidyverse)
library(lubridate)
load_objects("../Objects/")
load_objects("../Estimates objects/")
```

# Winter Troll

## Harvest

Low harvest in Early Winter NO, with a higher proportion of Early Winter harvest in NI and SI. Late Winter harvest was higher in NO than last year.
```{r winter_harvest, message=FALSE}
(winter_harvest <- read_csv("../Harvest Data/20191021_ft - Detailed Fish Tickets.csv") %>% 
  mutate(Month = month(`Date Fishing Ended`, label = TRUE, abbr = FALSE)) %>% 
  mutate(Fishery = case_when(Month %in% month.name[1:4] ~ "Late Winter",
                             Month %in% month.name[5] ~ "Spring Ret 1", 
                             Month %in% month.name[6] ~ "Spring Ret 2", 
                             Month %in% month.name[7] ~ "Summer Ret 1",
                             Month %in% month.name[8:9] ~ "Summer Ret 2",
                             Month %in% month.name[10:12] ~ "Early Winter"
                             )) %>% 
 mutate(Quadrant = case_when(District %in% c(113, 114, 116, 154, 156, 157, 181, 183, 189) ~ 171,
                             District %in% c(103, 104, 152) ~ 172,
                             District %in% c(109, 110, 111, 112, 115) ~ 173,
                             District %in% c(101, 102, 105, 106, 107, 108) ~ 174)) %>% 
  filter(Year == 2018 & Fishery == "Early Winter" | Year == 2019 & Fishery == "Late Winter") %>% 
  group_by(Quadrant, Fishery) %>% 
  summarise(Harvest = sum(`Number Of Animals (sum)`, na.rm = TRUE)) %>% 
  spread(Fishery, Harvest, fill = 0))
```

## Sample sizes

Final samples sizes for all Quadrant x Period. **Note** in all quadrants, we had to subsample in order to make everything proportional to harvest by stat week.
```{r winter_n}
winter_2019_sample_sizes %>% 
  separate(silly, into = c("Fishery", "Year"), sep = "_") %>% 
  select(Fishery, genotyped, missing, duplicate, final)
```

## Stock composition

For each Quadrant and Period there will be a table showing stock composition results for all major stocks (i.e. those contributing > 5% to harvest).  
**Note** Sample sizes for Early Winter are small given the limited harvest and subsampling.

### Early Winter - Northern Outside (171), Northern Inside (173), and Southern Inside (174)
What are the major stocks contributing to these mixtures (mean > 5%)? **Note** these sample sizes are all ~100 fish, so please take with a grain of salt!
```{r winter_stock_comp_table_EWintNO}
winter_2019_33RG_estimates.tdy %>% 
  mutate(value = value * 100) %>% 
  spread(estimator, value) %>% 
  filter(mean > 5 & fishery == "EWint" & quadrant != "SO") %>% 
  mutate_if(is.numeric, round, 1) %>% 
  arrange(quadrant, fishery, desc(mean)) %>% 
  select(fishery, quadrant, group, mean, sd, `5%`, `95%`)
```

Lower proportion of Columbia River stocks than last year.
```{r winter_troll_figures_EWintNO, fig.width=8, fig.height=8}
winter_2019_33RG_estimates.tdy %>% 
  spread(estimator, value) %>% 
  filter(fishery == "EWint" & quadrant != "SO") %>% 
  ggplot(aes(x = group, y = mean * 100)) +
  geom_col(fill = "lightblue") +
  geom_errorbar(aes(ymin = `5%` * 100, ymax = `95%` * 100)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  ylim(0, 100) +
  ylab("Stock Composition (%)") +
  xlab("Reporting Group") +
  ggtitle("Early Winter Troll AY 2019: Northern Outside 171") +
  facet_grid(quadrant ~ .)
```

### Early Winter - All Quadrants

What are the major stocks contributing to these mixtures (mean > 5%)?
```{r winter_stock_comp_table_EWintAllQuad}
winter_2019_33RG_stratified_estimates.tdy %>% 
  mutate(value = value * 100) %>% 
  spread(estimator, value) %>% 
  filter(mean > 5 & fishery == "EWint") %>% 
  mutate_if(is.numeric, round, 1) %>% 
  arrange(quadrant, fishery, desc(mean)) %>% 
  select(fishery, quadrant, group, mean, sd, `5%`, `95%`)
```

Much lower prevalence of Columbia River stocks and higher proportion of SSEAK stocks. This is partly due to the shift in harvest away from NO to NI and SI
```{r winter_troll_figures_EWintAllQuad, out.width="100%"}
winter_2019_33RG_stratified_estimates.tdy %>% 
  spread(estimator, value) %>% 
  filter(fishery == "EWint") %>% 
  ggplot(aes(x = group, y = mean * 100)) +
  geom_col(fill = "lightblue") +
  geom_errorbar(aes(ymin = `5%` * 100, ymax = `95%` * 100)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  ylim(0, 100) +
  ylab("Stock Composition (%)") +
  xlab("Reporting Group") +
  ggtitle("Early Winter Troll AY 2019: All Quad")
```

### Late Winter - Northern Outside (171), Northern Inside (173), and Southern Inside (174)

What are the major stocks contributing to these mixtures (mean > 5%)?  
**Note** sample sizes for NI and SI are much less than NO, so please take with a grain of salt!
```{r winter_stock_comp_table_LWintNONISI}
winter_2019_33RG_estimates.tdy %>% 
  mutate(value = value * 100) %>% 
  spread(estimator, value) %>% 
  filter(mean > 5 & fishery == "LWint" & quadrant != "SO") %>% 
  mutate(quadrant = factor(x = quadrant, levels = c("NO", "SO", "NI", "SI"))) %>% 
  mutate_if(is.numeric, round, 1) %>% 
  arrange(quadrant, fishery, desc(mean)) %>% 
  select(fishery, quadrant, group, mean, sd, `5%`, `95%`)
```

These stock compositions are more in line with what we saw last year.
```{r winter_troll_figures_LWintNONISI, fig.width=8, fig.height=8}
winter_2019_33RG_estimates.tdy %>% 
  spread(estimator, value) %>% 
  filter(fishery == "LWint" & quadrant != "SO") %>% 
  mutate(quadrant = factor(x = quadrant, levels = c("NO", "SO", "NI", "SI"))) %>%   ggplot(aes(x = group, y = mean * 100)) +
  geom_col(fill = "lightblue") +
  geom_errorbar(aes(ymin = `5%` * 100, ymax = `95%` * 100)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  ylim(0, 100) +
  ylab("Stock Composition (%)") +
  xlab("Reporting Group") +
  ggtitle("Late Winter Troll AY 2019: Quadrant") +
  facet_grid(quadrant ~ .)
```

### Late Winter - All Quadrants

What are the major stocks contributing to these mixtures (mean > 5%)?
```{r winter_stock_comp_table_LWintAllQuad}
winter_2019_33RG_stratified_estimates.tdy %>% 
  mutate(value = value * 100) %>% 
  spread(estimator, value) %>% 
  filter(mean > 5 & fishery == "LWint") %>% 
  mutate_if(is.numeric, round, 1) %>% 
  arrange(quadrant, fishery, desc(mean)) %>% 
  select(fishery, quadrant, group, mean, sd, `5%`, `95%`)
```

Overall picture for Late Winter is similar to last year. Most of the harvest is from WCVI and BC stocks + SSEAK in inside waters.
```{r winter_troll_figures_LWintAllQuad, out.width="100%"}
winter_2019_33RG_stratified_estimates.tdy %>% 
  spread(estimator, value) %>% 
  filter(fishery == "LWint") %>% 
  ggplot(aes(x = group, y = mean * 100)) +
  geom_col(fill = "lightblue") +
  geom_errorbar(aes(ymin = `5%` * 100, ymax = `95%` * 100)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  ylim(0, 100) +
  ylab("Stock Composition (%)") +
  xlab("Reporting Group") +
  ggtitle("Late Winter Troll AY 2019: All Quad")
```
