---
title: "Chinook Gillnet D183 2019"
output:
  html_notebook:
    theme: united
    toc: yes
editor_options: 
  chunk_output_type: inline
---

# Goals & Objectives



## Setup

Load *GCL-R-Functions* and all necessary packages.
```{r setup, message=FALSE, results='hide'}
source("~/../R/Functions.GCL.R")
library(tidyverse)
library(lubridate)

.username <- "krshedd"
.password <- ""
```

Read in those objects and `LocusControl`
```{r load_objects}
load_objects("../Objects/")
```

# Gillnet D183: import mixture genotypes

Read in genotypes from *LOKI* as `.gcl` objects. Save in directory.
```{r winter_loki}
yakutat_2019_mixnames <- "KGILL19D83"
LOKI2R_GAPS.GCL(sillyvec = yakutat_2019_mixnames, username = .username, password = .password)
rm(.username, .password)

sapply(yakutat_2019_mixnames, function(silly) {get(paste0(silly, ".gcl"))$n} )

save_sillys(sillyvec = yakutat_2019_mixnames, path = "../Genotypes/original")
```

# Data QA

Standard data QA:

  * Remove fish missing <80% genotypes
  * Remove duplicates (>95% genotype concordance)

```{r yakutat_QA}
yakutat_2019_mixnames <- "KGILL19D83"

# original sample sizes
yakutat_2019_sample_sizes <- tibble(silly = yakutat_2019_mixnames,
                                   genotyped = sapply(yakutat_2019_mixnames, function(x) {
                                     get(paste0(x, ".gcl"))$n
                                   }))

# missing
yakutat_2019_missing <-
  RemoveIndMissLoci.GCL(sillyvec = yakutat_2019_mixnames, proportion = 0.8)

save_objects("yakutat_2019_missing", "../Objects/")

yakutat_2019_sample_sizes <- yakutat_2019_sample_sizes %>%
  mutate(missing = genotyped - sapply(yakutat_2019_mixnames, function(x) {
    get(paste0(x, ".gcl"))$n
  }))

# duplicate
yakutat_2019_duplicates <-
  CheckDupWithinSilly.GCL(
    sillyvec = yakutat_2019_mixnames,
    loci = GAPSLoci_reordered,
    quantile = NULL,
    minproportion = 0.95
  )

(yakutat_2019_duplicates_summary <-
    sapply(yakutat_2019_mixnames, function(x) {
      yakutat_2019_duplicates[[x]]$report
    }))

save_objects("yakutat_2019_duplicates_summary", "../Objects/")

yakutat_2019_duplciates_removed <-
  RemoveDups.GCL(dupcheck = yakutat_2019_duplicates)

yakutat_2019_sample_sizes <- yakutat_2019_sample_sizes %>%
  mutate(duplicate = genotyped - missing - sapply(yakutat_2019_mixnames, function(x) {
    get(paste0(x, ".gcl"))$n
  }))

# final
yakutat_2019_sample_sizes <- yakutat_2019_sample_sizes %>%
  mutate(final = sapply(yakutat_2019_mixnames, function(x) {
    get(paste0(x, ".gcl"))$n
  }))

yakutat_2019_sample_sizes

save_objects("yakutat_2019_sample_sizes", "../Objects/")

write_csv(yakutat_2019_sample_sizes,
          "../Tables/yakutat_2019_sample_sizes.csv")
```

# Create *BAYES* files

## Directory setup

First need to set up *BAYES* directory structure and copy over baseline file and *BAYES* objects. This was already done when we ran TBR.


## Create mixtures

Save the fortran format and create TBR *BAYES* mixture files. This was already done when we ran TBR.
```{r spring_BAYES_mixtures}
# mixfortran <- CreateMixture.GCL(sillys = TBR_sillys[1], loci = GAPSLoci_reordered, IDs = NULL, mixname = TBR_mixnames[TBR_sillys[1]], dir = "../BAYES/Mixture", type = "BAYES", PT = FALSE)
# save_objects("mixfortran", "../Objects/")

CreateMixture.GCL(
  sillys = yakutat_2019_mixnames,
  loci = GAPSLoci_reordered,
  IDs = NULL,
  mixname = yakutat_2019_mixnames,
  dir = "../BAYES/Mixture",
  type = "BAYES",
  PT = FALSE
)
```

## Create control files

Now that we have priors, just need to create *BAYES* control files.
```{r spring_BAYES_control}
CreateControlFile.GCL(
  sillyvec = SEAKPops357,
  loci = GAPSLoci_reordered,
  mixname = yakutat_2019_mixnames,
  basename = "GAPS357pops13loci",
  suffix = "",
  nreps = 40000,
  nchains = 5,
  groupvec = GroupVec33RG_357,
  priorvec = flat_prior,
  initmat = GAPS357PopsInits,
  dir = "../BAYES/Control",
  seeds = WASSIPSockeyeSeeds,
  thin = c(1, 1, 100),
  mixfortran = mixfortran,
  basefortran = bayesfortran_357,
  switches = "F T F T F T F"
)
```

# Summarize *BAYES* results

Summarize results for both the full 33 reporting groups.

## 33 reporting groups

Create standard summary and save.
```{r spring_BAYES_summarise_33RG}
# full 33 reporting groups
Yakutat_2019_33RG_EstimatesStats <- 
  CustomCombineBAYESOutput.GCL(groupvec = 1:33, groupnames = GroupNames33, maindir = "../BAYES/Output", mixvec = yakutat_2019_mixnames,
                               prior = "", ext = "RGN", nchains = 5, burn = 0.5, alpha = 0.1, PosteriorOutput = FALSE)

# dir.create("../Estimates objects")
save_objects(c("Yakutat_2019_33RG_EstimatesStats"), "../Estimates objects")
```

```{r}
as_tibble(Yakutat_2019_33RG_EstimatesStats$KGILL19D83, rownames = "groups") %>% 
  arrange(desc(mean))
```

